---
title:  "DS01_6_4_RMarkdown.Rmd"
author: "Barton Poulson"
date:   "2016-03-23"
output: 
  html_document: 
    number_sections: yes
    toc: yes
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Inline R Code ###########################################

Inline code can be included in a sentence. It is marked off with single back-ticks and the letter "r" must occur after the first backtick, like this:

```{r backtick, eval = FALSE}
`r code`
```

For example, 3^2 + 1 = `r 3^2 + 1`. In this example, the equation is in Markdown but the result is inline R code:

## R Code Chunks ###########################################

Although it is possible to include R code inline, it is more common to use code chunks. There are three ways to insert code chunks in R Markdown:

1. With the menu: Code > Insert Chunk
1. With the keyboard shortcut: opt-cmd-I
1. Manually: Type three backticks -- ``` -- then {r}. Put code on new lines and close with a line with three more backticks.

# CREATING R MARKDOWN DOCUMENTS ############################

## Embedding Statistical Output ############################

This command runs basic descriptive statistics for the iris data that is included in R's datasets package.

```{r summary}
summary(iris)
```

## Embedding Plots #########################################

You can also embed plots, such as this default plot for the iris data:

```{r plot}
plot(iris)
```

## Knitting the Document ###################################

To run R Markdown code and create an R Markdown document, you need to "knit" the document. There are three ways to knit your document:

1. With the menu: File > Knit Document.
1. With the keyboard shortcut: shift-cmd-K.
1. With the menu button at the top of the document window.

# PUBLISHING TO RPUBS ######################################

To publish an R Markdown document to [RPubs.com](http://rpubs.com/), you first need to create a free account there. You will also need to install some additional packages to R when you publish your first document, but RStudio will do that automatically for you.

There are two ways to publish your document:

1. With the menu: File > Publish...
1. With the menu button at the top right of the document window.

You will then give the document a name and it will be publicly available on RPubs.

**Congratulations! You're published!**
